\bf Faster Neural Machine Translation Inference

### 2018-02-05 fast-beam/fast-beam.tex
fast beam paper

We shall leave step 1 for future work and focus on the last three steps, the outline for which are shown in Figures~\ref{algo:original-softmax-beamsearch}.

\begin{figure} 
\begin{algorithmic}

@@

\end{algorithmic}
\caption{Original Softmax and Beam Search Algorithm}
\label{algo:original-softmax-beamsearch}
\end{figure}

@@

Thirdly, we are only interested in the best class. Since the best class is known, we can avoid calculating softmax for all classes. The outline of the our function is shown in Figure~\ref{algo:Fused Kernel}.

\begin{figure} [h]
\begin{algorithmic}
\Procedure{Fused Kernel}{vector $p$, bias vector $b$}

@@

\caption{Fused softmax and argmax}
\label{algo:Fused Kernel}
\end{figure}

In fact, we are usually only interested in the best class during inference, not the probability. Therefore, we can skip the second iteration over $p$ in Figure~\ref{algo:Fused Kernel} and avoid computing the softmax altogether, Figure~\ref{algo:Argmax only}.

\begin{figure} [h]
\begin{algorithmic}
\Procedure{Find-1-Best}{vector $p$, bias vector $b$}

@@

\end{algorithmic}
\caption{Find 1 best only}
\label{algo:Argmax only}
\end{figure}

It has been shown ~\citep{koehn-knowles:2017:NMT} that using beam search to use the n-best number of classes, rather than just the best class, improves translation quality. This is a simple extension to the algorithm of Figure~\ref{algo:Fused Kernel}. Unlike the 1-best case, however, the softmax calculation cannot be skipped as the denominator differs for each input.

@@

The standard mini-batching algorithm is outlined in Figure~\ref{algo:Mini-batching}.

\begin{figure} [h]
\begin{algorithmic}
\Procedure{Mini-Batching}{}
%\REQUIRE source sentence $s$, translation options
\While{more input} 
  \State Create batch
  \State Encode(batch)
  \While{batch is not empty} 
    \State Decode(batch)
    \For{each sentence in batch}
      \If{translation is complete}
        \State Remove sentence %from batch
      \EndIf
    \EndFor
  \EndWhile
\EndWhile

@@

\end{algorithmic}
\caption{Mini-batching}
\label{algo:Mini-batching}
\end{figure}

@@

Our proposed top-up batching algorithm encode and decode asynchronously. The encoding step, Figure~\ref{algo:Encoding for top-up batching}, is similar to the main loop of the standard algorithm but the results are added to a queue to be consumed by the decoding step later.

\begin{figure} [h]
\begin{algorithmic}

@@

\end{algorithmic}
\caption{Encoding for top-up batching}
\label{algo:Encoding for top-up batching}
\end{figure}

Rather than decoding the same batch until all sentences in the batch are completed, the decoding step processing the same batch continuously. New sentences are added to the batch as old sentences completes, Figure~\ref{algo:Decoding for top-up batching}.

\begin{figure} [h]
\begin{algorithmic}

@@

\end{algorithmic}
\caption{Decoding for top-up batching}
\label{algo:Decoding for top-up batching}
\end{figure}

>>>>

We shall leave step 1 for future work and focus on the last three steps, the outline for which are shown in Algorithm~\ref{algo:original-softmax-beamsearch}.

\begin{algorithm} 
\begin{algorithmic}

@@

\end{algorithmic}
\caption{Original Softmax and Beam Search Algorithm}
\label{algo:original-softmax-beamsearch}
\end{algorithm}

@@

Thirdly, we are only interested in the best class. Since the best class is known, we can avoid calculating softmax for all classes. The outline of the our function is shown in Algorithm~\ref{algo:Fused Kernel}.

\begin{algorithm}
\begin{algorithmic}
\Procedure{Fused Kernel}{vector $p$, bias vector $b$}

@@

\caption{Fused softmax and argmax}
\label{algo:Fused Kernel}
\end{algorithm}

In fact, we are usually only interested in the best class during inference, not the probability. Therefore, we can skip the second iteration over $p$ in Algorithm~\ref{algo:Fused Kernel} and avoid computing the softmax altogether, Algorithm~\ref{algo:Argmax only}.

\begin{algorithm}
\begin{algorithmic}
\Procedure{Find-1-Best}{vector $p$, bias vector $b$}

@@

\end{algorithmic}
\caption{Find 1 best only}
\label{algo:Argmax only}
\end{algorithm}

It has been shown ~\citep{koehn-knowles:2017:NMT} that using beam search to use the n-best number of classes, rather than just the best class, improves translation quality. This is a simple extension to the algorithm of Algorithm~\ref{algo:Fused Kernel}. Unlike the 1-best case, however, the softmax calculation cannot be skipped as the denominator differs for each input.

@@

The standard mini-batching algorithm is outlined in Algorithm~\ref{algo:Mini-batching}.

\begin{algorithm}
\begin{algorithmic}
\Procedure{Mini-Batching}{}
%\REQUIRE source sentence $s$, translation options
\While{more input} 
  \State Create batch
  \State Encode(batch)
  \While{batch is not empty} 
    \State Decode(batch)
    \For{each sentence in batch}
      \If{translation is complete}
        \State Remove sentence %from batch
      \EndIf
    \EndFor
  \EndWhile
\EndWhile

@@

\end{algorithmic}
\caption{Mini-batching}
\label{algo:Mini-batching}
\end{algorithm}

@@

Our proposed top-up batching algorithm encode and decode asynchronously. The encoding step, Algorithm~\ref{algo:Encoding for top-up batching}, is similar to the main loop of the standard algorithm but the results are added to a queue to be consumed by the decoding step later.

\begin{algorithm}
\begin{algorithmic}

@@

\end{algorithmic}
\caption{Encoding for top-up batching}
\label{algo:Encoding for top-up batching}
\end{algorithm}

Rather than decoding the same batch until all sentences in the batch are completed, the decoding step processing the same batch continuously. New sentences are added to the batch as old sentences completes, Algorithm~\ref{algo:Decoding for top-up batching}.

\begin{algorithm}
\begin{algorithmic}

@@

\end{algorithmic}
\caption{Decoding for top-up batching}
\label{algo:Decoding for top-up batching}
\end{algorithm}
